Episodic memory: mental time travel or a quantum `memory wave' function?

### 2019-01-03 main.tex
working on reinstatement description-- Fig 2

Although the specific content of each moment of the episode is largely unique, participants' subjective experiences of the episode entail weaving together those temporally separated moments into a cohesive narrative.  This is reflected in how people verbally recount the episode later.  If we examine the temporal autocorrelation matrices of participants' recalls of the television episode (characterized using the same topic model used to capture the content of the episode; Figs.~\ref{fig:corrmats}B, C), we see a different structure than that of the episode itself.  Although individual participants' recalls exhibit periods of content stability punctuated by rapid change (block diagonal structure of the matrices in Fig.~\ref{fig:corrmats}C), the off diagonal correlations between temporally distant events are substantially stronger in participants' recalls than in the original episode.  This indicates that the way participants \textit{recount} temporally separated events imposes additional similarity on those events.  One might then ask \textbf{JRM STOPPED HERE}
%where i was going with this: is that structure meaningful?  one can ask which specific events are described similarly (reinstatement fig).  argument: yes, the structure is meaningful-- example: the way people describe the particular event (sherlock surmising a new murder has happened between bantering with Watson) is similar to how participants describe the other murders and other sherlock/watson banterings

\begin{figure}[tp] \centering \includegraphics[width=\textwidth]{figs/reinstatement} \caption{\textbf{Mental time travel in random word lists and video.}  }
  % colors: individual participants
  % black: average across participants
  % gray: autocorrelation with topic vector at timepoint
  % circles: local maxima in the across-participants average (i.e., movie events that share structure with the given timepoint that is distinct from other temporally proximal events)
\label{fig:reinstatement}
\end{figure}

>>>>

Although the specific content of each moment of the episode is largely unique, participants' subjective experiences of the episode entail weaving together those temporally separated moments into a cohesive narrative.  This is reflected in how people verbally recount the episode later.  If we examine the temporal autocorrelation matrices of participants' recalls of the television episode (characterized using the same topic model used to capture the content of the episode; Figs.~\ref{fig:corrmats}B, C), we see a different structure than that of the episode itself.  Although individual participants' recalls exhibit periods of content stability punctuated by rapid change (block diagonal structure of the matrices in Fig.~\ref{fig:corrmats}C), the off diagonal correlations between temporally distant events are substantially stronger in participants' recalls than in the original episode.  This indicates that the way participants \textit{recount} temporally separated events imposes additional similarity on those events, beyond what was present in the original events themselves.  Is this simply a matter of imprecision in recall, either with respect to participants' recalls themselves, or with respect to the quality with which they are characterized via semantic feature vectors?  Or might there be a functional role to that additional imposed similarity structure?

To examine which specific events are described (during recall) as more similar than what their original experiences (as characterized by semantic feature vectors) would suggest, it can be helpful to examine individual recalls of particular events throughout the episode.  \textbf{JRM STOPPED HERE...}

%where i was going with this: is that structure meaningful?  one can ask which specific events are described similarly (reinstatement fig).  argument: yes, the structure is meaningful-- example: the way people describe the particular event (sherlock surmising a new murder has happened between bantering with Watson) is similar to how participants describe the other murders and other sherlock/watson banterings

\begin{figure}[tp] \centering \includegraphics[width=\textwidth]{figs/reinstatement} \caption{\textbf{Content drift in a television episode and participants' recalls of that episode.  A.  Autocorrelations in the episode's content and in the content of participants' recalls.}  The black line denotes the average correlations between the topic vectors from pairs of moments in the episode as a function of their temporal separation (times are relative to the full length of the episode).  Each colored line denotes an analogous autocorrelation function, but for each individual participant's recalls of the episode (times are relative to the full length of each participant's recalls).  The error ribbons denote 95\% confidence intervals, taken across all moments in the episode (or in participants' recalls of the episode).  \textbf{B. Recall density functions for one recalled moment.} Each curve reflects the correlations between the topic vector at each (relative) moment of the episode (or participants' recalls of the episode), and the topic vector of an event beginning approximately $\frac{1}{3}$ through the episode (relative time: 0.328).  The gray curve denotes these correlations for the topic vectors derived from annotations of the episode itself. \textbf{JRM STOPPED HERE...}}
  % colors: individual participants
  % black: average across participants
  % gray: autocorrelation with topic vector at timepoint
  % circles: local maxima in the across-participants average (i.e., movie events that share structure with the given timepoint that is distinct from other temporally proximal events)
\label{fig:reinstatement}
\end{figure}
